### 2012-08-23 intention motor representation joint action (paper 3)/conf collective intentionality manchester 2012/motor representation and shared intention.tex
manchester talk

\def \ititle {Intention and Motor Representation in Joint Action}
\def \isubtitle {}
\def \iauthor {S. Butterfill* \& C. Sinigaglia**
\\ 
**Department of Philosophy, University of Warwick
\\ 
***Dipartimento di Filosofia, Università degli Studi di Milano}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

@@

\begin{abstract}
\noindent
On the assumption that motor representation plays a role in explaining how effective joint action is possible, is there also a role for motor representation in explaining what joint action is?  
Philosophers tend to assume that motor representation is only an enabling condition for joint action and of no direct interest to narrowly philosophical theories of joint action and shared intention.  In this paper we identify a certain structure of motor representations---call it \textit{social motor representation}---which can enable joint action,
and we argue that social motor representation and shared intention  have distinctive roles in explaining the purposiveness of joint action.  This gives rise to a challenge.  On the one hand, effective joint action---imagine two people erecting a tent in a gale together---sometimes requires both shared intentions and social motor representations plus a certain kind of harmony between the two.  On the other hand, recognizing their distinctive roles precludes the existence of direct inferential links between shared intentions and social motor representations.  The challenge is to explain how these two kinds of representation could sometimes harmoniously contribute to effective joint action despite the lack of inferential integration.
\end{abstract}

\section{Introduction}
Which events are joint actions?
We shall argue that fully answering this question involves appeal to structures of motor representation.
By contrast, 
most philosophers and many (but not all) psychologists appear to assume that this question can be fully answered just in terms of a special kind of intention or structure of intention, knowledge and committment often called a shared (or `collective') intention.
On this widely held view, for an event to be a joint action is for it to be appropriately related to a shared intention.
This view is analogous to the view that, in the case of ordinary, individual action, 
 for an event to be an action is for it to be appropriately related to an intention.

Few have argued for, or objected to, 
the view that for an event to be a joint action is for it to be appropriately related to a shared intention.
This is striking because the parallel assumption about ordinary, individual action is not universally accepted. 
In fact, some allow that there could be agents whose actions are purposive---and, in some cases, even intentional---although  the agents have no intentions at all.%
\footnote{
For instance, \citet[p.\ 251]{bratman:2000_valuing} % = \citep[p.\ 51]{Bratman:2007bd}
describes an agent called `Creature 2' who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally'.
}
And others have argued that motor representation and intention are both needed in explaining which events are ordinary, individual actions \citep{butterfill:2012_intention}.
If any such view is correct, it is impossible to fully explain what it is for an event to be an action by appeal to intention alone.
Our aim is to provide material for a parallel view about joint action.
We shall offer considerations in favour of two claims: 
First, fully explaining which events are joint actions requires appeal to structures of motor representation and not only to shared intention.
%***what's the argument for this second claim!?
And, second, recognising a constitutive role for motor representation in joint action makes possible an account of shared intention which is simpler and more elegant than any of the leading alternatives.

Note that the main claims of this paper are arguably consistent  with the claim that for an event to be an action is for it to be appropriately related to an intention.
This is because it is possible to reject the claim that joint actions are actions. 
Indeed, \citet[p.\ 376]{ludwig_collective_2007} has offered an independent reason to reject this claim.
Suppose we accept, following \citet[pp.\ 49, 59]{Davidson:1971fz}, that all actions are bodily movements.
Or suppose we follow \citet{hornsby_actions_1980} in holding that actions are tryings. 
Then it turns out that few or no paradigm cases of joint action are actions.
In making the sauce, one agent stirs while the other pours;
in painting the house, one covers the outside while the other does the inside; 
and in walking together each walker moves her own legs.
In each of these supposedly paradigm cases of joint action, as in many others, no bodily movements which are actions (and no tryings) need have two or more agents.
Apparently, then, joint actions are not actions. 
This raises the possibility that the ingredients involved in explaining which events are actions differ from those involved in explaining which events are joint actions.
Ludwig's observation on joint actions not being actions 
also suggests, more generally, that caution is needed in generalising claims about ordinary, individual action to include joint action. 
Although we shall draw parallels between individual and joint action, such parallels will serve merely exegetical ends.

In what follows we aim to extend and generalise existing theories, not to replace them.
We take for granted that some notion of shared intention is needed for explaining which events are joint actions. 
Our aim is only to show that additional ingredients are needed by characterising one such ingredient.

\section{Social motor representation}
We start from the premise that reciprocal agent-neutral motor representation enables some joint actions.
This needs unpacking.
A representation (motor or not) is \emph{agent-neutral} if its content does not specify any agent or agents.%
\footnote{
Our use of the term `agent-netural' to describe motor representations bears no relation to the use of the same term  to describe reasons \citep[on the latter, see][]{Parfit:1984fk}.
}
To illustrate, agent neutral representations are sometimes found at the early stages of planning.
Imagine that you and some friends are tasked with preparing a holiday.  
You might first write down a plan of action without specifying who will act; the plan simply describes what is to be done.
The plan  will eventually be implemented by you and your friends
 but this is not written in plan itself  and so it is agent-neutral.
Of course the fact that this plan is your collective plan may be represented elsewhere; this fact may also be implicit in  the plan's being stapled to the door of your communal kitchen.
The agent-neutrality of a representation does not require that the agents are nowhere specified, only that they are not specified in the content of the representation.\footnote{
Strictly the following argument does not hinge on the agent-neutrality of representations.
It is sufficient for our purposes that there are reciprocal motor representations which concern actions which are partly but not entirely the agent's own.
In principle such representations could have contents which specify other agents or multiple agents.
We focus on agent-neutral representations to simplify exposition.
}
Two or more agents have \emph{reciprocal} motor representations  just if there is a single outcome and each agent has a motor representation of that outcome.
We shall use the term \emph{social} motor representation as an abbreviation for reciprocal agent-neutral motor representation.
(Of course we cannot assume in advance of argument that reciprocal agent-neutral motor representations are social in any interesting sense;
but we are using the term `social' in a non-standard way as an abbreviation, one that reflects our aim.)
So for two or more agents to have social motor representation is just for there to be a single outcome of which each agent has an agent-neutral motor representation.

Our premise is just that social motor representation is among the factors enabling some joint actions.
It does not follow that social motor representation is involved in every joint action,
nor that the existence of social motor representation would be sufficient for there to be joint action.

This premise is doubly controversial.
While it is now well established both that there are motor representations of action outcomes (and not merely patterns of joint displacement, say), and also that there are motor representations of the outcomes of others' actions rather than only of one's own actions,
less research has so far considered the conjecture that motor representations concern outcomes of actions which are partly but not entirely one's own.
There is also relatively little evidence for the further conjecture that such representations enable some joint actions.
We shall not argue for either conjecture; they are empirical premises.  
What follows is speculative philosophy: an attempt to explain the consequences and significance of the conjecture that social motor representation enables some joint actions.

Why even consider the premise that social motor representation enables joint action?
A direct way to test the premise would be to 
measure how (if at all) selective interventions on social motor representation affected agents’ performance of joint actions.
As far as we know no one has done this and it may be impractical.
But there are some indirect findings.
We shall focus on just one, which will serve to illustrate the premise (but does not provide a decisive reason to accept it).
Kourtis and colleagues report that `[s]imulation of another person’s action, as reflected in the activation of motor cortices, gets stronger the more the other is perceived as an interaction partner’  \citep[p.\ 4]{kourtis:2010_favoritism}.
To establish this they had two subjects sit opposite each other at a table; there was also a confederate at the table, the `loner'.  
Sometimes the subjects acted alone, picking up and replacing an object.  And sometimes they had to act together, passing an object between them.  
The loner always acted alone.
EEG measurements of motor activation were recorded.
The researchers compared patterns of motor activation in four conditions: when the first subject acted, when the second subject acted, when the loner acted and when there was a `no go' signal so that no one acted.
They found that when one of the subjects acted, patterns of activation in each of the two subjects were similar regardless of which was acting and which was observing.
By contrast, when the loner acted the subjects' patterns of activation resembled those found in the `no go' condition when there was no action.
Since the researchers did not include a condition where there was a competitive, non-joint interaction, we cannot conclude that the effect they found is specific to joint action as opposed to other kinds of interaction.
What we do take this paper to indicate, 
together with a body of other research on motor representation of observed action,
is this.
If you are engaged in a joint action with someone, one which involves moving an object by passing it between you, then each of you has motor representations of actions whose (perhaps improper) components include actions which will be performed by the other  and these motor representations are functionally equivalent to motor representations of your own actions in the sense that they are just the sorts of representation that might have caused you to do what the other is doing if you were in her position.

For each of the agents involved in a joint action to represent motorically actions whose (perhaps improper) components include the others' action is not yet for there to be social motor representation.
For there to be social motor representation there must be an outcome (such as the movement of an object from one place to another) which each agent has an agent-neutral motor representation of.
The experiment by \citet{kourtis:2010_favoritism} was not designed to distinguish
cases in which each agent represents the outcome to which the  whole joint action is directed (in this case, the entire movement of the object)
from
 cases in which 
each agent represents separately outcomes to which each of the individual actions comprising the joint action (in this case, the several movements of the object each of which just one agent is responsible for).
We are making a leap and assuming (without argument) that in cases like that studied by Kourtis and colleagues, there is sometimes social motor representation.

\section{How could social motor representation enable joint action?}
Suppose that social motor representation is present in some joint action contexts, and, inspired by \citet{kourtis:2010_favoritism}, that 
social motor representations are more likely to occur in joint action than when one is merely observing.
It doesn't follow, of course, that social motor representation enables some joint actions.
But let us consider just the possibility that it might.
How could social motor representation enable joint action even in principle?

@@

How is this relevant to the case of joint action?
In joint action the agents have the same goal, to move the object from one place to another.
They also face a similar coordination problem, requiring a precisely timed swap from one hand to another.
Now suppose, 
inspired by Koutis et al’s and others' findings,
that the same planning is involved in the individual case (where one agent performs the whole action) and in the joint action case (where the action is distributed between two agents).
The planning is the same almost up to the actual muscle contractions.
How could this be helpful?
Suppose the agents' planning processes are similar enough that, for a given context and problem, they will produce approximately the same plans.
Then having each agent plan the whole joint action means that (i) each agent plans the other agent's action,
(ii) each agent's plan for the other agent's action is approximately the same as that agent's plan for her own action,
and 
(iii) each  agent's plans for their own action are constrained by their plans for the other agent's action.
So what enables the two agents' plans to mesh is not that they represent each other's plans but more simply that they plan each other's actions as well as their own actions as if they were each about to do the whole thing themselves.
Each agent is planning (and monitoring) both their actions almost as if a single agent were going to execute the whole action.
And of course this is exactly what we want for small-scale joint action---we want two or more agents to act as one.
This may be why the performance of dyads in joint actions often resembles the performance of individuals tasked with performing the whole action alone (*refs: Knoblich circles following task).

@@

\section{Grounding the purposiveness of joint action}
So far we have only been considering a possible role for social motor representation in enabling joint action.  
Our primary concern, though, is with what joint action is.
The details of how 
social motor representation enables joint action
 already give us grounds for holding that motor representation has a role to play in explaining which events are joint actions.
To see why,
let’s go back to individual action for a moment again.

@@

\section{The Contrast Cases}

\section{Social motor representation: unlike shared intention}

*function (not to coordinate planning in Bratman's sense)

*format (based on earlier paper ...)

\section{***Joint action without shared intention}
Our opening question was, Which events are joint actions?
The standard view is that for an event to be a joint action it must be appropriately related to a shared intention.
We are in the process of arguing that this is not the whole truth about joint action,
and that some events are joint actions by virtue of being appropriately related to a structure of motor representations we call social motor representation.
We don’t mean to suggest that all joint actions involve social motor representation.
The view we are aiming to establish is rather this: Some joint actions involve social motor representation; and there could be joint actions which involve social motor representation but not shared intention.
This is why 
%Recap: the question was: Does social motor representation  play a role in explaining what joint is?
%I have just been arguing for a positive answer.
%My thesis is this:
%\textbf{Reciprocal agent-neutral motor representations coordinate multiple agents’ actions around an outcome in part by virtue of representing that outcome.}
%That is, reciprocal social motor representations can ground the purposiveness of joint action.
%This is why I think that 
fully understanding what joint action is requires understanding the coordinating role of social motor representation and not only understanding shared intention.

%*Two lines of objection:
%(1) all joint actions involve share intention [here]
%(2) social motor representation is just a species of shared intention (have just been filling in some details of how shared intentions are realised). [later]
We are some way off having argued for this view.
One consequence of our view is that there could be joint actions without shared intention. 
But this does not straightforwardly follow from the claim we have argued for, namely that social motor representation is involved in some joint actions.
And it also goes against a widely held view.
To focus on just one case, Alonso says `the key property of joint action lies in its internal component [...] in the participants' having a ``collective'' or ``shared'' intention' \citep[pp.\ 444-5]{alonso_shared_2009}.%
\footnote{
***others
}
%Now for all we have said so far, 
%someone might allow that, as we have argued, social motor representation is involved in some joint actions 
%but also insist that all joint actions involve shared intention.
If this were right, it would be false or at least unclear that social motor representation is needed to answer the question about which events are joint actions.
We must therefore defend the view that joint action need not involve shared intention.

As far as we know, the claim that all joint action involves shared intention is not explicitly argued for.  
The best argument we know of hinges on so-called contrast cases.
Contrast cases are pairs of actions which are similar in terms of behaviour and coordination but where one is joint but the other isn't.  
\citet{gilbert_walking_1990} contrasts two people walking together with two people individually walking side by side.  
The two pairs' movements may be the same and similarly coordinated (to avoid collision), but walking together is a joint action whereas merely walking side by side is not. 
Relatedly,  \citet{Searle:1990em}  contrasts a case in which several park visitors simultaneously run to a central shelter in order to perform a dance with another case in which the park visitors run to the central shelter in order to escape a storm.  The first is a case of joint action, the second is not; but the same movements occur in both.  
These sorts of contrast case invite the question, 
How do joint actions differ from individual but parallel actions? 
Gilbert’s example shows that the difference can’t just be a matter of coordination, because people who are merely walking alongside each other also need to coordinate their actions in order to avoid colliding.  
And Searle’s example shows that the difference between joint action and parallel individual action can’t just be that the actions have a common effect because merely parallel actions can have common effects too.

How could the contrast cases be used to argue that all joint action involves shared intention?
The argument rests on this premise:
It is possible to distinguish systematically between the contrast cases by appeal to shared intention and only by appeal to shared intention.
To defeat this argument we shall show that there is another, more general way to distinguish contrast cases.

Take Searle's example of several people running to the shelter.  
In the joint case, there is a single outcome to which each person's actions is individually directed, namely their collective arrival at the shelter.  
In the contrasting individual case, where park visitors individually run to the shelter to escape a storm, there is no single outcome to which each of their actions is individually directed.  
Instead each visitor's actions are directed to that visitor's own arrival at the shelter.  
Similarly, turning to Gilbert's example, when two people walk together, there is a single outcome to which both of their actions are individually directed (their collective arrival at a corner, say); whereas when two people merely walk side by side there is no single outcome to which each agent's actions are directed.  
In general, where two or more agent's actions constitute a joint action, there is an outcome to which each agent's actions are individually directed such that it is possible for them all to succeed relative to this outcome.%
\footnote{
Some readers may be sceptical of this claim.
But note that it is a consequence of the view we are opposing, the view that all joint actions involve shared intention.
Or, rather, it is a consequence of this view given a further premise which is a consequence of any standard account of shared intention: Where several agents act on a shared intention that they J, 
each will perform an action directed to J and it is possible for them all to succeed in J-ing.
} 
Since this is not true in the contrasting cases of non-joint action, it allows us to distinguish systematically between joint actions and their non-joint but behaviourally and coordinatively indistinguishable counterparts.

For concision let us stipulate that an outcome is a \emph{distributive goal} of two or more agents' actions just if two conditions are met.
First, this outcome is a goal to which each agent's actions are individually directed.
Second, each agent's actions are related to the goal in such a way that it is possible for all the agents (not just any agent, all of them together) to succeed relative to this goal.
Let us also say that a structure is \emph{something like shared intention} if it stands to joint action roughly as intention stands to ordinary, individual action.  
In these terms, our claim is that joint actions involve distributive goals and that this distinguishes joint actions from non-joint actions in the standard contrast cases.  
Given that the existence of a distributive goal need involve nothing like a shared intention, we can conclude that systematically distinguishing between the contrast cases does not require anything like shared intention.

I think this argument is mistaken for two reasons.

\section{Slide}
First because there are contrast cases in which the joint action does not involve shared intention.
For instance, contrast our lifting a sofa together with us each individually raising either end of the sofa, coincidentally at the same time.
The former is a joint action whereas the latter is arguably not.
But I don't think it's right to assume that lifting a sofa together necessarily involves shared intention (although our \emph{buying} a sofa together might).
So it seems to me that the contrast cases give us no reason at all to suppose that all joint actions involve shared intention.

In fact the existence of cases like the sofa indicate that appeal to shared intention does not provide a sufficiently general way of explaining the difference illustrated by the contrast cases.

This brings me to a second consideration.
There is a more general notion appeal to which enables us to distinguish the contrast cases.
Genuine joint action differs from merely parallel action because the former involves each agent’s representing an outcome to which all of their actions are directed where these outcome representations coordinate their actions in a way that would normally facilitate their collective success in bring about this outcome.

>>>>

\def \ititle {Motor Representation and Shared Intention}
\def \isubtitle {}
\def \iauthor {
%S. Butterfill* \& C. Sinigaglia**
%\\ 
%**Department of Philosophy, University of Warwick
%\\ 
%***Dipartimento di Filosofia, Università degli Studi di Milano
}
\def \iemail{s.butterfill@warwick.ac.uk}
%\date{}

@@

\begin{abstract}
\noindent
On the assumption that motor representation plays a role in explaining how effective joint action is possible, do we also need motor representation to explain what joint action is? Philosophers tend to assume that motor representation is only an enabling condition for joint action and of no direct interest to narrowly philosophical theories of joint action and shared intention. In this talk I shall argue that social motor representation and shared intention have distinctive roles in explaining the purposiveness of joint action. This gives rise to a challenge. On the one hand, effective joint action—imagine two people erecting a tent in a gale together—sometimes requires both shared intentions and social motor representations plus a certain kind of harmony between the two. On the other hand, recognizing their distinctive roles precludes the existence of direct inferential links between shared intentions and social motor representations. The challenge is to explain how these two kinds of representation could sometimes harmoniously contribute to effective joint action despite the lack of inferential integration. 
\end{abstract}

\section{Introduction}
Which events are joint actions?
Most philosophers and many (but not all) psychologists appear to assume that this question can be fully answered just in terms of a special kind of intention or structure of intention, knowledge and commitment often called a shared (or `collective') intention.
On this widely held view, for an event to be a joint action is for it to be appropriately related to a shared intention.

[\textit{Short version: One consideration in favour of this view is ... and jump to the second consideration towards the end of  section \ref{text:second_consideration} on page \vpageref{text:second_consideration}.}]

\subsection{What is shared intention?}
Of course this answer to the question about which events are joint actions assumes that we know what shared or collective intention is.
But there are many accounts of it.
Still, I think most people would agree that shared intention stands to joint action approximately as plain vanilla intention stands to ordinary, individual action
Further,
on all or most leading accounts of shared intention, each of the following is a necessary condition:

\begin{description}

\item[awareness of joint-ness] Agents acting on a shared intention know that they are not acting individually; they have `a conception of themselves as contributors to a collective end.'\footnote{
	\citet[p.\ 10]{Kutz:2000si}.  Compare \citet[p.\ 361]{Roth:2004ki}: `each participant ... can answer the question of what he is doing or will be doing by saying for example ``We are walking together'' or ``We will/intend to walk together.''' 
Relatedly, \citet[p. 56]{miller_social_2001} requires that each agent believes her actions are interdependent with the other agent's.
}

\item[awareness of others' agency]  When agents act on a shared intention, each is aware of at least one of the others as an intentional agent.\footnote{
	Compare \citet[p.\ 333]{Bratman:1992mi}: `Cooperation ... is cooperation between intentional agents each of whom sees and treats the other as such'.  See also \citet[p.\ 105]{Searle:1990em}: `The biologically primitive sense of the other person as a candidate for shared intentionality is a necessary condition of all collective behavior' 
}

\item[awareness of others' states or commitments] When two agents share an intention that they F, each is aware of, or has individuating beliefs about, some of the other's intentions, beliefs or commitments concerning F.\footnote{
This condition is necessary for shared intention even on what \citet[p.\ 40]{tuomela_collective_2000} calls `the weakest kind of collective intention'.  But it may not be necessary if, as \citet{Gold:2007zd} suggest, shared intentions are constitutively intentions formed by a certain kind of reasoning.
% "if the distinctive feature of collective intentions is to be found in the reasoning by which they were formed, then an analysis that focuses on the intentions themselves will miss the feature that makes collective intentions collective. " 
}

\end{description}
%
I think we can go even further and say that, 
on most accounts,
where joint action involves shared intention, the agents act in part \emph{because} of their awareness of joint-ness, of others' agency and of others' states or commitments.

What follows assumes that where one or more of these three conditions is not met, there is no shared intention.

\subsection{Why shared intention?}
Why might anyone hold that for an event to be a joint action is for it to be appropriately related to a shared intention?
Two considerations favour this view.

First, the view might be motivated by appeal to some well-known contrast cases.
Contrast cases are pairs of events which are similar in terms of the behaviour and coordination they involve but where one is a joint action while the other is not.  
Thus \citet{gilbert_walking_1990} contrasts two people walking together with two people individually walking side by side.  
The two pairs' movements may be the same and similarly coordinated (to avoid collision), but walking together is a joint action whereas merely walking side by side is not. 
Relatedly,  \citet{Searle:1990em}  contrasts a case in which several park visitors simultaneously run to a central shelter in order to perform a dance with another case in which the park visitors run to the central shelter in order to escape a storm.  The first is a case of joint action, the second is not; but the same movements occur in both.  
These sorts of contrast case invite the question, 
How do joint actions differ from individual but parallel actions? 
Gilbert’s example shows that the difference can’t just be a matter of coordination, because people who are merely walking alongside each other also need to coordinate their actions in order to avoid colliding.  
And Searle’s example shows that the difference between joint action and parallel individual action can’t just be that the actions have a common effect because merely parallel actions can have common effects too. 
If someone thought that it is possible to distinguish systematically between the contrast cases by appeal to shared intention (and perhaps only by appeal to shared intention), this could motivate holding that for an event to be a joint action is for it to be appropriately related to a shared intention.

{\label{text:second_consideration} A second consideration} in favour of this view is a possible parallel between shared intention and ordinary, individual action.
If you think that events are actions in virtue of being appropriately related to intentions, 
and if you think that shared intention stands to joint action as plain vanilla intention stands to ordinary, individual action,
then it seems reasonable to suppose that for an event to be a joint action is for it to be appropriately related to a shared intention (*cite Pacherie Synthese forthcoming).

\subsection{My view}
But the parallel assumption about ordinary, individual action is not universally accepted. 
In fact, some allow that there could be agents whose actions are purposive---and, in some cases, even intentional---although  the agents have no intentions at all.
For instance, Michael Bratman describes a creature who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally'.%
\footnote{
For instance, \citet[p.\ 251]{bratman:2000_valuing} % = \citep[p.\ 51]{Bratman:2007bd}
describes an agent called `Creature 2' who `acts on the basis of its beliefs and considered desires' only (not intentions) as doing things `intentionally'.
}
Others have argued that motor representation and intention are both needed in explaining which events are ordinary, individual actions \citep{pacherie:2000_content,butterfill:2012_intention}.
If any such view is correct, it is impossible to fully explain what it is for an event to be an action by appeal to intention alone.

Our aim in this talk is to defend a parallel view about joint action. 
%(Parallel to the latter view, that is: not saying that creatures without any shared intentions are capable of joint actions.)
We shall consider the possibility that fully explaining which events are joint actions requires appeal to structures of motor representation and not only to shared intention.
%***what's the argument for this second claim!?

Please bear in mind that we are not trying to get rid of, or replace, the notion of shared intention.
%I take for granted that a notion of shared intention is needed for explaining which events are joint actions. 
%My concern is only with the possibility that additional ingredients are needed as well.
In fact recognising that motor representation is needed to say which events are joint actions may make it easier to understand what shared intention is.

\section{Social motor representation}
We start from the premise that some joint actions are facilitated by reciprocal, agent-neutral motor representations of outcomes whose obtaining would normally involve action on the part of each agent.

This needs unpacking. 
A \textit{motor} representation is the sort of representation that enables us to reach for, grasp and transfer objects in a coordinated and fluid way.
We follow several psychologists and philosophers in supposing that motor representations feature in planning and monitoring action \citep[e.g.]{wolpert:1995internal, miall:1996_forward}.
One consequence is that motor representations are not concerned with merely kinematic or dynamic features of actions only.
Rather, some motor representations represent outcomes, such as the movement of a target object from one place to another.

A representation (motor or not) is \emph{agent-neutral} if its content does not specify any agent or agents.%
\footnote{
Our use of the term `agent-netural' to describe motor representations bears no relation to the use of the same term  to describe reasons \citep[on the latter, see][]{Parfit:1984fk}.
}
To illustrate, agent neutral representations are sometimes found at the early stages of planning.
Imagine that you and some friends are tasked with preparing a holiday.  
You might first write down a plan of action without specifying who will act; the plan simply describes what is to be done.
The plan  will eventually be implemented by you and your friends
 but this is not written in plan itself  and so it is agent-neutral.
Of course the fact that this plan is your collective plan may be represented elsewhere; this fact may also be implicit in  the plan's being stapled to the door of your communal kitchen.
The agent-neutrality of a representation does not require that the agents are nowhere specified, only that they are not specified in the content of the representation.%
\footnote{
Strictly the following argument does not hinge on the agent-neutrality of representations.
It is sufficient for our purposes that there are reciprocal motor representations  of outcomes whose obtaining would normally involve action on the part of each of the reciprocating agents.
In principle such representations could have contents which specify other agents or multiple agents. 
We focus on agent-neutral representations to simplify exposition.
It may be important that our view is consistent with the possibility that reciprocal motor representations are agent-neutral. 
}

Two or more agents have \emph{reciprocal} motor representations  just if there is a single outcome and each agent has a motor representation of that outcome. 
It is hardly controversial that reciprocal motor representations exist, for their existence is suggested by by a large body of research on motor cognition in action observation.
What is much more controversial is that reciprocal motor representation occurs in joint action.
Some of the research that Gunether Knoblich presented supports the claim that there are reciprocal motor representations in joint action, and he suggests that these enable joint action.%
\footnote{
See \citet{kourtis:2012_predictive}: `the partner’s expected action is simulated at the motor level, which probably facilitates effective performance of the joint action.'
\citet{kourtis:2010_favoritism} show that 
reciprocal motor representation is more likely to occur in joint action than is mere observation. 
See also \citet{Knoblich:2003nf}.
 }

I want to go a tiny step further and suggest that in joint action there are sometimes reciprocal, agent-neutral representations of outcomes whose obtaining would normally involve action on the part of all of the agents.
So when we act together, some of my motor representations may concern outcomes that are partly but not entirely to be realised by my actions.
For example, suppose our task is to move an object from A to B, where you pick it up and pass it to me so that I can then place it.
In this case I may represent the movement of the object from A to B and not only the component movements.
I represent a collective outcome of our actions and not just outcomes to which each of our actions are individually directed.
%
%So it is not just that, when we act together, I represent the outcomes to which your actions are directed and the outcomes to which my actions are directed; I may also represent an outcome to which all of our actions are directed.

We shall use the term \emph{social} motor representation as an abbreviation for the reciprocal, agent-neutral motor representation of outcomes whose obtaining would normally require action on the part of each reciprocating agent.
(Of course we cannot assume in advance of argument that such reciprocal, agent-neutral motor representations are social in any interesting sense;
but we are using the term `social' in a non-standard way as an abbreviation, one that reflects our aim.)

What follows is speculative philosophy: we take for granted that sometimes social motor representation facilitates joint action and ask whether this conjecture bears on our question about which events are joint actions.

\section{How could social motor representation facilitate joint action?}
Suppose that social motor representation is present in some joint action contexts.
It doesn't follow, of course, that social motor representation facilitates some joint actions.
But let us consider just the possibility that it might.
How could social motor representation facilitate joint action even in principle?

@@

How is this relevant to the case of joint action?
In joint action the agents have the same goal, to move the object from one place to another.
They also face a similar coordination problem, requiring a precisely timed swap from one hand to another.
Now suppose, 
inspired by Koutis et al’s and others' findings,
that the same planning is involved in the individual case (where one agent performs the whole action) and in the joint action case (where the action is distributed between two agents).
The planning is the same almost up to the actual muscle contractions.

How could this be helpful?
Suppose the agents' planning processes are similar enough that, for a given context and problem, they will produce approximately the same plans.
Then having each agent plan the whole joint action means that (i) each agent plans the other agent's action,
(ii) each agent's plan for the other agent's action is approximately the same as that agent's plan for her own action,
and 
(iii) each  agent's plans for their own action are constrained by their plans for the other agent's action.

So what enables the two agents' plans to mesh is not that they represent each other's plans but more simply that they plan each other's actions as well as their own actions as if they were each about to do the whole thing themselves.

Each agent is planning (and monitoring) both their actions almost as if a single agent were going to execute the whole action.
And of course this is exactly what we want for small-scale joint action---we want two or more agents to act as one.
This may be why the performance of dyads in joint actions often resembles the performance of individuals tasked with performing the whole action alone \citep{Knoblich:2003nf}.

@@

\section{Grounding the purposiveness of joint action}
So far we have only been considering a possible role for social motor representation in facilitating joint action.  
Our primary concern, though, is with what joint action is.
The details of how 
social motor representation enables joint action
 already give us grounds for holding that motor representation has a role to play in explaining which events are joint actions.
To see why,
let’s go back to individual action for a moment again.

@@

%
%\section{The Contrast Cases}
%We have been arguing that social motor representation can bind multiple agents' activities together and link them to an outcome, and this in much the way that shared intention does  so.
%This is a reason, 
%not decisive but perhaps sufficient in the absence of strong contrary reasons, 
%for supposing that social motor representation plays a role in explaining which events are joint actions.
%Perhaps some events are joint actions in virtue of being appropriately related not to shared intention but to social motor representation.
%
%As mentioned at the start, our aim is to extend and generalise existing theories, not to replace them. 
%But at this point our answer to the question of which events are joint actions seems to involve a disjunction.
%This is both puzzling and inelegant. 
%(Unless, of course, social motor representation can be regarded as a special case of shared intention.  
%We explain why we reject this possibility below.)
%In this section we explain how an account of joint action in terms of shared intention can be generalised to accommodate the possibility that social motor representation plays a role in explaining which events are joint actions.
%
%What guides and constrains theorising about shared intention? 
%While there is little agreement on what shared intention is or what it is for, intuitions about it are sometimes grounded in contrast cases.
%Contrast cases are pairs of events which are similar in terms of the behaviour and coordination they involve but where one is a joint action while the other is not.  
%Thus \citet{gilbert_walking_1990} contrasts two people walking together with two people individually walking side by side.  
%The two pairs' movements may be the same and similarly coordinated (to avoid collision), but walking together is a joint action whereas merely walking side by side is not. 
%Relatedly,  \citet{Searle:1990em}  contrasts a case in which several park visitors simultaneously run to a central shelter in order to perform a dance with another case in which the park visitors run to the central shelter in order to escape a storm.  The first is a case of joint action, the second is not; but the same movements occur in both.  
%These sorts of contrast case invite the question, 
%How do joint actions differ from individual but parallel actions? 
%Gilbert’s example shows that the difference can’t just be a matter of coordination, because people who are merely walking alongside each other also need to coordinate their actions in order to avoid colliding.  
%And Searle’s example shows that the difference between joint action and parallel individual action can’t just be that the actions have a common effect because merely parallel actions can have common effects too. 
%
%How might the contrast cases be used to guide and constrain theorising about shared intention?
%The idea that they serve this function seems to rest on a premise:
%It is possible to distinguish systematically between the contrast cases by appeal to shared intention and only by appeal to shared intention.
%We shall show that there is another, more general way to distinguish contrast cases.
%
%Take Searle's example of several people running to the shelter.  
%In the joint case, there is a single outcome to which each person's actions is individually directed, namely their collective arrival at the shelter.  
%In the contrasting individual case, where park visitors individually run to the shelter to escape a storm, there is no single outcome to which each of their actions is individually directed.  
%Instead each visitor's actions are directed to that visitor's own arrival at the shelter.  
%Similarly, turning to Gilbert's example, when two people walk together, there is a single outcome to which both of their actions are individually directed (their collective arrival at a corner, say); whereas when two people merely walk side by side there is no single outcome to which each agent's actions are directed.  
%In general, where two or more agent's actions constitute a joint action, there is an outcome to which each agent's actions are individually directed such that it is possible for them all to succeed relative to this outcome.%
%\footnote{
%Some readers may be sceptical of this claim.
%But note that it is a consequence of the view we are opposing, the view that all joint actions involve shared intention.
%Or, rather, it is a consequence of this view given a further premise which is a consequence of any standard account of shared intention: Where several agents act on a shared intention that they J, 
%each will perform an action directed to J and it is possible for them all to succeed in J-ing.
%} 
%Since this is not true in the contrasting cases of non-joint action, it allows us to distinguish systematically between joint actions and their non-joint but behaviourally and coordinatively indistinguishable counterparts.  
%
%For concision let us stipulate that an outcome is a \emph{distributive goal} of two or more agents' actions just if two conditions are met.
%First, this outcome is a goal to which each agent's actions are individually directed.
%Second, each agent's actions are related to the goal in such a way that it is possible for all the agents (not just any agent, all of them together) to succeed relative to this goal.
%In these terms, our claim is that joint actions involve distributive goals and that this distinguishes joint actions from non-joint actions in the standard contrast cases.  
%Since social motor representation and shared intention are each sufficient for the existence of a distributive goal, we can conclude that systematically distinguishing between standardly considered contrast cases does not require shared intention.
% 
%A natural response to this argument would be to suggest that the standard contrast cases are insufficient. 
%For in some cases two agents' actions can have a distributive goal although arguably there is no joint action. 
%Nora and Olive killed Fred.  
%Each fired a shot.
%Each intended that her shooting ground or partially ground Fred's death.%
%\footnote{
%Events $D_1$, ...\ $D_n$ \emph{ground} $E$, if: $D_1$, ...\ $D_n$ and $E$ occur; 
%$D_1$, ...\ $D_n$ are each part of $E$; and 
%every event that is 
%	a part of $E$
%	but does not overlap $D_1$, ...\ $D_n$ 
%is caused by some or all of $D_1$, ...\ $D_n$.
%(This is a refinement and generalisation of a notion due to \citet{pietroski_actions_1998}.)
%Event $D$ \emph{partially grounds} event $E$ if $D$ alone does not ground $E$ but there are events including $D$ which do ground $E$.
%} 
%%
%As it turned out, both intentions were fulfilled.
%Neither shot was individually fatal but together they were deadly.
%An ambulance arrived on the scene almost at once but Fred didn't make it to the hospital.
%Now Nora and Olive's actions have a distributive goal.
%After all, 
%	each agent's actions are individually directed to Fred's death
%	and  
%	it is consistent with the stipulations made about this scenario that these goal relations are compatible in the sense that both agents could succeed together. 
%But is their killing of Fred a joint action?
%Imagine that Nora and Olive had no knowledge of each other, nor of each other's actions, and that their efforts were entirely uncoordinated.
%We might even suppose that Nora and Olive are so antagonistic to each other that they would, if either knew the other's location, turn their guns on each other.
%Their actions nevertheless have a distributive goal.
%But given these further suppositions it is likely to seem counterintuitive to suppose that their killing Fred was a joint action. 
%So although we can distinguish the standardly considered contrast cases just by appeal to the notion of a distributive goal, we should not assume that this notion captures the intended contrast between joint and merely parallel actions.
%
%***HERE refine: collective goals
%
%
%
%\section{Social motor representation: unlike shared intention}
%
%*function (not to coordinate planning in Bratman's sense)
%
%*format (based on earlier paper ...)
%
